A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
Gam predicted conversion for percent disease severity

```{r}
PM_dat_D$yi_percent <- ((PM_dat_D$PM_final_severity)/median(PM_dat_D$PM_final_severity) * 100)
PM_dat_D$vi_percent <- PM_dat_D$vi/median(PM_dat_D$PM_final_severity)
hist(PM_dat_D$yi_percent)
summary(PM_dat_D$yi_percent)
```

>>>>

```{r}
# Disease response ratio
# create column giving the respective disease severity in the control 
PM_dat_D$yi_C <- unlist(apply(PM_dat_D, 1, function(x1){

   mean(PM_dat_D[PM_dat_D$trial == x1[["trial"]] &
               PM_dat_D$spray_management == "control", "PM_final_severity"])
}))

# Calculate response ratio
PM_dat_D$yi_RR <- PM_dat_D$PM_final_severity/PM_dat_D$yi_C
hist(PM_dat_D[PM_dat_D$spray_management != "control", "yi_RR"])

# Log response ratio 
PM_dat_D$yi_LR <- log(PM_dat_D$yi_RR)
hist(PM_dat_D[PM_dat_D$spray_management != "control", "yi_LR"])

# Percent severity conversion
# define ordinal conversion from scale to proportion
s1 <- 0
s2 <- 0.33*0.5
s3 <- 0.5*0.87
s4 <- 0.66*0.75
s5 <- 0.66*0.87
s6 <- 0.66*1
s7 <- 0.75*1
s8 <- 1*0.87
s9 <- 1*1
x <- c(s1, s2, s3, s4, s5, s6, s7, s8, s9)
y <- c(1:9)
a = data.frame(x,y)
plot(a)

# fit a curve using a gam with spline value 0.2
g1 <- gam(x ~ s(y,spar = 0.1))

# View plot of gam
plot(x = predict(g1, data.frame(y= seq(1,9, by =0.1))), y= seq(1,9, by =0.1))
points(x,y,col = "red", pch = 16)

# predict values for dataset
new_sev <- predict(object =  g1, 
                   newdata = data.frame(y = PM_dat_D[,"PM_final_severity"])
                   )
# inspect distribution
hist(new_sev)
PM_dat_D$yi_percent <- new_sev

# Conversion of variance
# Here I add the variance and mean severity and predict the conversion value
# then subtract the mean severity to obtain the difference as the sample variance
PM_dat_D$vi_percent  <- predict(object =  g1, 
                   newdata = data.frame(y = PM_dat_D[,"vi"] + PM_dat_D[,"PM_final_severity"])
                   ) - PM_dat_D$yi_percent

# campare untransformed variance to transformed variance
summary(PM_dat_D$vi)
summary(PM_dat_D$vi_percent)
PM_dat_D[10:12,]
```
